\documentclass[10pt,a4paper]{article}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[margin=1.3cm]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{array}
\usepackage{tabularx}

\setlength{\parindent}{0pt}
\setlength{\parskip}{2pt}
\setlist[itemize]{leftmargin=1.1em, itemsep=1pt, topsep=1pt}
\setlength{\tabcolsep}{0pt}
\setlength{\emergencystretch}{2em}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\vspace{-0.2em}\rule{\linewidth}{0.4pt}]
\titlespacing*{\section}{0pt}{0.4em}{0.25em}

\newcommand{\cvgroupgap}{\vspace{0.7em}}

\newcommand{\cvrole}[4]{
	\begin{tabular*}{\linewidth}{@{\extracolsep{\fill}}lr}
		\textbf{#1} & #2\\
		\textit{#3} & \textit{#4}\\
	\end{tabular*}\\[-0.35em]
}

\begin{document}
\raggedright

{\LARGE \textbf{Bishal Adhikari}}\\
London, United Kingdom \;|\; 07832 549712 \;|\; \href{mailto:ezbishal@gmail.com}{ezbishal@gmail.com}

\section*{Professional Summary}
Software Engineer with 5+ years of experience building and scaling business-critical web, API, and mobile applications across logistics and digital services. Expert in C\#, .NET, JavaScript/TypeScript, React, SQL Server, and Azure. Proven track record of owning end-to-end delivery, improving production reliability, and shipping secure integrations that support high-volume operations.

\section*{Technical Skills}
{\renewcommand{\arraystretch}{1.16}
\begin{tabularx}{\linewidth}{>{\bfseries}p{2.25cm}X}
Backend & C\#, .NET, ASP.NET, JavaScript, TypeScript, Node.js, REST APIs, OAuth 2.0 \\
Frontend & React, Blazor, HTML5, CSS3, Tailwind, Bootstrap \\
Mobile & .NET MAUI, React Native, Expo \\
Cloud &  Azure API Management, Azure AD B2C, Key Vault, Azure SQL \\
DevOps & Azure DevOps, GitHub Actions, CI/CD, Agentic workflow automation \\
Data & SQL Server, SQLite, LINQ, Entity Framework \\
Power & Power BI, Power Automate, Power Apps \\
Quality & Unit testing, Integration testing, Application Insights, Agile Scrum, Git \\
\end{tabularx}
}

\section*{Professional Experience}
\cvrole{Software Engineer}{Mar 2023 -- Present}{Rhenus Logistics}{London, United Kingdom}
\begin{itemize}
	\item Led end-to-end delivery across 8 business-critical logistics systems, including internal tools, customer portal, customer API, warehousing scanner, POD mobile app, ERP module, reporting services, and scheduled background services.
	\item Engineered full-stack features using C\#, .NET, Blazor, React, SQL Server, and Azure to streamline warehouse and freight workflows.
	\item Built mobile capabilities with .NET MAUI and React Native (Expo), enabling field teams to complete core operational tasks on the move.
	\item Architected secure cloud integrations with Azure API Management, Key Vault, Storage Accounts, Azure Functions, and Azure App Registrations.
	\item Automated build and release pipelines in Azure DevOps, improving deployment consistency and reducing release risk across multiple products.
	\item Implemented reporting and workflow automation with Power BI, Power Automate, and Power Apps, increasing operational visibility and reducing manual processing.
	\item Strengthened production reliability by creating Application Insights dashboards, proactive alerts, and resilient API error-handling patterns.
	\item Partnered with product, operations, and architecture stakeholders to translate complex requirements into scalable, maintainable solutions delivered in Agile sprints.
\end{itemize}

\cvgroupgap

\cvrole{Junior .NET Developer}{Nov 2019 -- Nov 2021}{Yodha.US}{Kathmandu, Nepal}
\begin{itemize}
	\item Developed and maintained a backend .NET web application (C\#, ASP.NET MVC, SQL Server) supporting customer-facing counselling journeys and internal operations.
	\item Delivered features for a React Native (Expo) mobile app used by 5M+ users across Google Play and the iOS App Store.
	\item Built and maintained REST APIs and third-party integrations using OAuth 2.0 and token-based authentication to support secure partner connectivity.
	\item Optimized SQL Server queries and schema design to improve application performance and data reliability.
	\item Increased release quality through unit testing, regression validation, and production support in high-traffic scenarios.
	\item Collaborated in Agile sprints with product and engineering teams to ship incremental, user-focused enhancements.
\end{itemize}

\newpage

\section*{Certifications}
\textbf{Microsoft Certified: Azure AZ-900} \hfill 2024\\
\textit{Microsoft}\\
\begin{itemize}
	\item Validated foundational cloud knowledge across IaaS, PaaS, and SaaS models, Azure global infrastructure, and shared responsibility principles.
	\item Demonstrated understanding of core Azure services including compute, networking, storage, identity and access management, and governance capabilities.
	\item Covered Azure pricing, cost management, security, privacy, compliance, and lifecycle support concepts used in enterprise cloud delivery.
\end{itemize}

\section*{Education}
\textbf{MSc, Information Systems} \hfill 2022 -- 2023\\
\textit{University of Greenwich} \hfill \textit{London, United Kingdom}\\
\vspace{0.15em}
System Architecture, Enterprise Application Development, Cloud Systems, Mobile Development, IT Governance and Compliance, Data Modelling

\vspace{0.5em}

\textbf{BSc, Computer Science} \hfill 2014 -- 2019\\
\textit{Tribhuvan University} \hfill \textit{Kathmandu, Nepal}\\
\vspace{0.15em}
Data Structures and Algorithms, Object-Oriented Programming, Database Systems, Software Engineering, Artificial Intelligence, Operating Systems

\section*{References}
References available upon request.

\end{document}
